Submission HW1

### 2022-08-30 hw1-1/submission.Rmd
minor analysis notes

---
title: "Submission HW1"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

@@

[**#Analysis:**]{style="color:red"}
**There are 190 support vectors, or roughly 30% of the total data points.

@@

### v1: Equation of SVM
$W = \sum_i(\alpha Y_i X_{support\_vector_i})$$

>>>>

---
title: "Submission HW1"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

@@

[**#Analysis:**]{style="color:red"} \*\*There are 190 support vectors, or roughly 30% of the total data points.

@@

### Final SVM Model and it's equation

$W = \sum_i(\alpha Y_i X_{support\_vector_i})$

```{r}
modelf = ksvm(x=as.matrix(org_cc_data[,1:10]), y=org_cc_data[,11], scaled =TRUE, type = "C-svc",kernel = "vanilladot", C = 0.0015)
acc_func(modelf)

a <- colSums(modelf@xmatrix[[1]] * modelf@coef[[1]])
a0 <- -modelf@b
a
a0
```
[**#Analysis:**]{style="color:red"}

## Question 2.2 (part 2: kSVM with Non Linear kernel)

We have tried 2 kernels:

1.  Radial Basis, and

2.  Laplace

### Non Linear models: Radial Basis Kernel
```{r}
C_values <- c(0.01,1,10,50,100,1000,2000)

for (C_i in C_values) {
  print (paste("For C = ",C_i))
  modeli = ksvm(x=as.matrix(org_cc_data[,1:10]), y=org_cc_data[,11], scaled =TRUE, type = "C-svc",kernel = "rbfdot", C = C_i)
  acc_func(modeli)
  print(modeli@nSV)
}
```

### Non Linear models: Laplace Kernel
```{r}
C_values <- c(0.01,1,10,50,100,1000,2000)

for (C_i in C_values) {
  print (paste("For C = ",C_i))
  modeli = ksvm(x=as.matrix(org_cc_data[,1:10]), y=org_cc_data[,11], scaled =TRUE, type = "C-svc",kernel = "laplacedot", C = C_i)
  acc_func(modeli)
  print(modeli@nSV)
}
```
